---
title: "Multiple Score Comparison with `mscpredmodel` - a typical analysis workflow"
author: "Sarah R Haile, PhD"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multiple Score Comparison with mscpredmodel - a typical analysis workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Typical analysis

This is a basic example which shows you a typical analysis for a dataset having individual patient data for 30 cohorts, each with some combination of scores a, b, c, e, and g. The example here has only 25 bootstrap samples to speed up the runtime, but an actual analysis should use more.

```{r msc_setup}
library(mscpredmodel)
library(ggplot2)
theme_set(theme_bw())

dat <- msc_sample_data()
dat
M <- 25
bs.example <- get_bs_samples(data = dat, id = id, cohort = study, 
                             outcome = outcome, n.samples = M, 
                             scores = c("a", "b", "c", "e", "g"), 
                             moderators = c("age", "female"))
```

We want to examine performance of the 5 scores according to calibration-in-the-large. We show a basic analysis for calibration-in-the-large, and then repeat the analysis with calibration slope. Note that we use the same set of bootstrap samples for each of the performance measures, so that any differences in variability are due only to the performance measures themselves, and not because of differing bootstrap samples.

## Calibration-in-the-large
```{r example1}
ps <- compute_performance(bs.example, fn = calibration_large, 
                          lbl = "calibration-in-the-large")
lines(ps)

agg <- aggregate_performance(ps, reference = "b")
check_transitivity(agg, graph = TRUE)

modc <- consistency(agg)
modi <- inconsistency(agg)
modi

check_transitivity(agg)
check_homogeneity(modi)

allpairs <- msc_network(ps)
plot(allpairs)
```

## Calibration slope

```{r example2}
ps2 <- compute_performance(bs.example, fn = calibration_slope, lbl = "calibration slope")
lines(ps2)

agg2 <- aggregate_performance(ps, reference = "b")
check_transitivity(agg2, graph = TRUE)

mod2c <- consistency(agg2)
mod2i <- inconsistency(agg2)
mod2i

check_homogeneity(mod2i)
check_consistency(ps2)
check_transitivity(agg2)

allpairs2 <- msc_network(ps2)
plot(allpairs2, compare_to = "c")
```

